---
title: "Data cleaning and transformations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(stringr)
library(geosphere)
library(tidytext)
library(textdata)
library(gender)
```


## Raw data

Let's load the raw data.

```{r}
raw_data = read.csv("AB_NYC_2019.csv")
```

We focus our analysis on listings for short-term stays, defined as with 6 day or less minimum stay, and only consider listings with at least one review. We also remove listings with a price higher than 1000$.

```{r}
data = raw_data %>% 
  filter(minimum_nights < 7, 
         number_of_reviews > 0, 
         price <= 5000)
```

## Reviews per month

We compute the number of months a listing has been inactive as the number of months between the listing's last review and the end of the time frame under consideration by the data ("2019-07-08"). This is then used to deduce the number of months the listing has been active, and to define the normalized average number of reviews per month as 

```{r}
data = data %>% mutate(last_review = ymd(last_review),
                       months_inactive = as.numeric(ymd("2019-07-08") - last_review)/30.42,
                       months_active = (number_of_reviews - reviews_per_month * months_inactive) / 
                         reviews_per_month) %>% 
  mutate(months_active = case_when(
    months_active >= 1 ~ round(months_active), 
    months_active < 1 ~ 1
  )) %>% 
  mutate(nrml_avg_reviews = case_when(
    reviews_per_month > 0 ~ number_of_reviews/months_active,
    is.na(reviews_per_month) ~ 0
    ))
```

## Distance to closest subway station

We also compute the distance (in meters) from a listing to the closest subway station using Subway entrance data from NYC's Open Data project (https://data.cityofnewyork.us/Transportation/Subway-Entrances/drex-xx56).

```{r}
subways = read.csv("subways.csv")
subways = subways[,"the_geom"] %>% 
  str_remove_all("POINT ") %>% 
  str_remove_all("[\\(\\)]") %>% 
  str_split(" ")

subways = sapply(subways, function(x) {
  c(as.numeric(x[[1]]), as.numeric(x[[2]]))
})

lambd <- Vectorize(function(long, lat) {
  min(apply(subways, 2, function(s) {
    #distHaversine(c(long, lat), c(s[1], s[2]))
    x = lat - s[2]
    y = (long - s[1]) * cos((lat + s[2])*0.00872664626)  
    111.319 * sqrt(x*x + y*y) * 1000
  }))
})

dists = lambd(data$longitude, data$latitude)

data = data %>% mutate(dist_to_subway = dists)
```


## Gender

```{r}
host_names = data[,"host_name", drop=F] %>% 
  mutate(name = as.character(host_name))

genders_data = gender(unique(host_names$name))
genders_data = data.frame(name = genders_data$name, 
                gender = case_when(genders_data$proportion_female > 0.90 ~ "Female",
                    genders_data$proportion_female > 0.10 ~ "Unknown",
                    TRUE ~ "Male")
)

data = data %>% mutate(gender=
                        sapply(as.character(data$host_name), function(x) {
                          i = which(genders_data$name == x)
                          if (length(i) > 0){
                            return(genders_data[i[[1]],2])
                          }
                          return(3)
                        }))

data = data %>% mutate(gender=case_when(gender==1 ~ "Female",
                                        gender==2 ~ "Male",
                                        TRUE ~ "Unknown"))
```


## Adjectives matrix

```{r}
data("stop_words")

text <- tolower(data$name)
text_df <- tibble(line = 1: dim(data)[1], text=text)

tidy_text <- text_df %>%  #Remove Stop Words
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_text_adj <- tidy_text %>% #Identify words with frequency >= 10
  left_join(parts_of_speech) %>%
  filter(pos %in% c("Adjective","Adverb")) %>%
  count(word, sort= TRUE) %>%
  filter(n >=10) %>%
  pull(word)

#Adjective matrix
adj_matrix <- matrix(NA, nrow = dim(data)[1], ncol = length(tidy_text_adj))

for(i in 1:length(tidy_text_adj)){
  adj_matrix[,i] <- str_detect(text, tidy_text_adj[i])
}

colnames(adj_matrix) <- tidy_text_adj
```

```{r}
dat = cbind(data, adj_matrix)
```

## Saving the results

```{r}
saveRDS(dat, "data_transformed.rds")
```



## Experimentation

```{r}
dat = readRDS("data_transformed.rds")

dat = dat %>% mutate(worth = price * nrml_avg_reviews)
```

```{r}
whole = seq(25, 1000, by=25)
less = whole + 1

dat %>% filter(price %in% whole) %>% summarise(n(), mean(nrml_avg_reviews))
dat %>% filter((price %in% less)) %>% summarise(n(), mean(nrml_avg_reviews))
```


```{r}
library(randomForest)

rf = randomForest(worth ~ minimum_nights + 
               availability_365 +
               latitude + 
               longitude +
               dist_to_subway +
                 factor(dat$room_type), data=dat)
```

```{r}
varImpPlot(rf)
```



```{r}
devtools::install_github("associatedpress/aptheme")
```

```{r}
library(aptheme)
library(tidyverse)

library(ggplot2)
library(aptheme)

```




















