---
title: "Final Neighborhood Distance Analysis"
author: "Justin Weltz"
date: "2/1/2020"
output: pdf_document
---
```{r}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(ggplot2)
require(CARBayes)
require(sp)
require(spdep)
require(StatMatch)
require(cluster)
```

Data

```{r}
data <- readRDS("data_transformed.rds")
#View(data)
```

```{r}
data %>% filter( neighbourhood == "Theater District" |neighbourhood == "Hell's Kitchen") %>% ggplot(aes(x  = latitude, y = longitude, color = neighbourhood)) + stat_density2d(aes(fill = ..level..), geom= "polygon")

data %>% filter(neighbourhood == "Chinatown") %>% ggplot(aes(x  = latitude, y = longitude)) + stat_density2d(aes(fill = ..level..), geom= "polygon")
```

Bronx Analysis
```{r}
set.seed(3)
data_bronx <- data %>% filter(neighbourhood_group == "Bronx") %>% dplyr::select(nrml_avg_reviews, price, neighbourhood, dist_to_subway, longitude, latitude)
```

Calculate Max Distance to One Neighbor and Create Adjacency Matrix
```{r}
data_clust <- data_bronx
  
points <- SpatialPoints(cbind(data_clust$latitude, data_clust$longitude))
Sy8_nb <- knearneigh(points, longlat = T, k = 1)

Sy8_nb <- knn2nb(Sy8_nb)

dsts <- unlist(nbdists(Sy8_nb, points))
min <- max(dsts)


dup <- which(duplicated(data_clust %>% dplyr::select(longitude, latitude)))

if(length(dup > 0)){
data_clust <- data_clust[-dup, ]
}

latlon <- data_clust %>% dplyr::select(longitude, latitude)

euclidean_dist <- daisy(latlon, metric = "euclidean")

euclidean_mat <- as.matrix(euclidean_dist)
dim(as.matrix(euclidean_dist))


adjacency <- matrix(0, ncol(euclidean_mat), ncol(euclidean_mat))
for (i in 1:ncol(euclidean_mat)){
  for (j in 1:ncol(euclidean_mat)){
    if (euclidean_mat[i,j] < min/1.7 ){
      adjacency[i,j] = 1
    }
  }
}
mean(rowSums(adjacency))
```


Run the Model

```{r}

new_data_clust <- data_clust %>% dplyr::select(-latitude, -longitude)

#summary(lm(nrml_avg_reviews~ neighbourhood, data = new_data_clust))

mod<- lm(nrml_avg_reviews ~ ., data = new_data_clust)

model_data <- model.matrix(mod)

#model_data

model_data <- cbind(new_data_clust$nrml_avg_reviews, model_data)

model_data <- data.frame(model_data)

#model_data

#View(model_data[,-2])

#memory.limit(size = 20000)
ref_bronx <- model_data[,-2]

#model_data
#dim(adjacency)

model_1_bronx <- S.CARleroux(data = model_data[-2], formula = V1 ~ ., family="gaussian", W= adjacency, burnin=1000, n.sample=200000, thin=10)


model_2_bronx <- S.glm(data =  model_data[-2], formula = V1 ~ ., family="gaussian", burnin=1000, n.sample=200000, thin=10)

summary(lm(data= new_data_clust, nrml_avg_reviews ~ .))


print(model_1_bronx)
print(model_2_bronx)
coef(model_1_bronx) - coef(model_2_bronx)


#Z.price <- as.matrix(dist(new_data_clust$price, diag=TRUE, upper=TRUE))

#model_3 <- S.CARdissimilarity(data = model_data[-2], formula = V1 ~ ., family="gaussian", W= adjacency, Z= list(Z.price =Z.price), W.binary = TRUE, burnin=1000, n.sample=100000, thin=10)
#model_3

```



Manhattan Analysis
```{r}
set.seed(3)
data_man <- data %>% filter(neighbourhood_group == "Manhattan") %>% dplyr::select(nrml_avg_reviews, price, neighbourhood, dist_to_subway, longitude, latitude) %>% sample_n(1000)
```

Calculate Max Distance to One Neighbor and Create Adjacency Matrix
```{r}
data_clust <- data_man
  
points <- SpatialPoints(cbind(data_clust$latitude, data_clust$longitude))
Sy8_nb <- knearneigh(points, longlat = T, k = 1)

Sy8_nb <- knn2nb(Sy8_nb)

dsts <- unlist(nbdists(Sy8_nb, points))
min <- max(dsts)


dup <- which(duplicated(data_clust %>% dplyr::select(longitude, latitude)))

if(length(dup > 0)){
data_clust <- data_clust[-dup, ]
}

latlon <- data_clust %>% dplyr::select(longitude, latitude)

euclidean_dist <- daisy(latlon, metric = "euclidean")

euclidean_mat <- as.matrix(euclidean_dist)
#dim(as.matrix(euclidean_dist))


adjacency <- matrix(0, ncol(euclidean_mat), ncol(euclidean_mat))
for (i in 1:ncol(euclidean_mat)){
  for (j in 1:ncol(euclidean_mat)){
    if (euclidean_mat[i,j] < min ){
      adjacency[i,j] = 1
    }
  }
}
mean(rowSums(adjacency))
```


Run the Model

```{r}

new_data_clust <- data_clust %>% dplyr::select(-latitude, -longitude)

#summary(lm(nrml_avg_reviews~ neighbourhood, data = new_data_clust))

mod<- lm(nrml_avg_reviews ~ ., data = new_data_clust)

model_data <- model.matrix(mod)

#model_data

model_data <- cbind(new_data_clust$nrml_avg_reviews, model_data)

model_data <- data.frame(model_data)

#model_data

#View(model_data[,-2])

#memory.limit(size = 20000)
ref_man <- model_data[,-2]

#model_data
#dim(adjacency)

model_1_man <- S.CARleroux(data = model_data[-2], formula = V1 ~ ., family="gaussian", W= adjacency, burnin=1000, n.sample=200000, thin=10)


model_2_man <- S.glm(data =  model_data[-2], formula = V1 ~ ., family="gaussian", burnin=1000, n.sample=200000, thin=10)

summary(lm(data= new_data_clust, nrml_avg_reviews ~ .))


print(model_1_man)
print(model_2_man)
coef(model_1_man) - coef(model_2_man)


#Z.price <- as.matrix(dist(new_data_clust$price, diag=TRUE, upper=TRUE))

#model_3 <- S.CARdissimilarity(data = model_data[-2], formula = V1 ~ ., family="gaussian", W= adjacency, Z= list(Z.price =Z.price), W.binary = TRUE, burnin=1000, n.sample=100000, thin=10)
#model_3

```



Queens Analysis
```{r}
set.seed(3)
data_queens <- data %>% filter(neighbourhood_group == "Queens") %>% dplyr::select(nrml_avg_reviews, price, neighbourhood, dist_to_subway, longitude, latitude) %>% sample_n(1000)
data_queens %>% group_by(neighbourhood) %>% summarise(mean = mean(nrml_avg_reviews))
```

Calculate Max Distance to One Neighbor and Create Adjacency Matrix
```{r}
data_clust <- data_queens
  
points <- SpatialPoints(cbind(data_clust$latitude, data_clust$longitude))
Sy8_nb <- knearneigh(points, longlat = T, k = 1)

Sy8_nb <- knn2nb(Sy8_nb)

dsts <- unlist(nbdists(Sy8_nb, points))
min <- max(dsts)


dup <- which(duplicated(data_clust %>% dplyr::select(longitude, latitude)))

if(length(dup > 0)){
data_clust <- data_clust[-dup, ]
}

latlon <- data_clust %>% dplyr::select(longitude, latitude)

euclidean_dist <- daisy(latlon, metric = "euclidean")

euclidean_mat <- as.matrix(euclidean_dist)
dim(as.matrix(euclidean_dist))


adjacency <- matrix(0, ncol(euclidean_mat), ncol(euclidean_mat))
for (i in 1:ncol(euclidean_mat)){
  for (j in 1:ncol(euclidean_mat)){
    if (euclidean_mat[i,j] < min/3 ){
      adjacency[i,j] = 1
    }
  }
}
mean(rowSums(adjacency))
```


Run the Model

```{r}

new_data_clust <- data_clust %>% dplyr::select(-latitude, -longitude)

#summary(lm(nrml_avg_reviews~ neighbourhood, data = new_data_clust))

mod<- lm(nrml_avg_reviews ~ ., data = new_data_clust)

model_data <- model.matrix(mod)

#model_data

model_data <- cbind(new_data_clust$nrml_avg_reviews, model_data)

model_data <- data.frame(model_data)

#model_data

#View(model_data[,-2])

#memory.limit(size = 20000)
ref_queens <- model_data[,-2]

#model_data
#dim(adjacency)

model_1_queens <- S.CARleroux(data = model_data[-2], formula = V1 ~ ., family="gaussian", W= adjacency, burnin=1000, n.sample=200000, thin=10)


model_2_queens <- S.glm(data =  model_data[-2], formula = V1 ~ ., family="gaussian", burnin=1000, n.sample=200000, thin=10)

summary(lm(data= new_data_clust, nrml_avg_reviews ~ .))


print(model_1_queens)
print(model_2_queens)
coef(model_1_queens) - coef(model_2_queens)


#Z.price <- as.matrix(dist(new_data_clust$price, diag=TRUE, upper=TRUE))

#model_3 <- S.CARdissimilarity(data = model_data[-2], formula = V1 ~ ., family="gaussian", W= adjacency, Z= list(Z.price =Z.price), W.binary = TRUE, burnin=1000, n.sample=100000, thin=10)
#model_3

```




Brooklyn Analysis
```{r}
set.seed(5)
data_brook <- data %>% filter(neighbourhood_group == "Brooklyn") %>% dplyr::select(nrml_avg_reviews, price, neighbourhood, dist_to_subway, longitude, latitude) %>% sample_n(2000)
data_brook %>% group_by(neighbourhood) %>% summarise(mean = mean(nrml_avg_reviews))
```

Calculate Max Distance to One Neighbor and Create Adjacency Matrix
```{r}
data_clust <- data_brook
  
points <- SpatialPoints(cbind(data_clust$latitude, data_clust$longitude))
Sy8_nb <- knearneigh(points, longlat = T, k = 1)

Sy8_nb <- knn2nb(Sy8_nb)

dsts <- unlist(nbdists(Sy8_nb, points))
min <- max(dsts)


dup <- which(duplicated(data_clust %>% dplyr::select(longitude, latitude)))

if(length(dup > 0)){
data_clust <- data_clust[-dup, ]
}

latlon <- data_clust %>% dplyr::select(longitude, latitude)

euclidean_dist <- daisy(latlon, metric = "euclidean")

euclidean_mat <- as.matrix(euclidean_dist)
dim(as.matrix(euclidean_dist))


adjacency <- matrix(0, ncol(euclidean_mat), ncol(euclidean_mat))
for (i in 1:ncol(euclidean_mat)){
  for (j in 1:ncol(euclidean_mat)){
    if (euclidean_mat[i,j] < min/2.5 ){
      adjacency[i,j] = 1
    }
  }
}
mean(rowSums(adjacency))
```


Run the Model

```{r}

new_data_clust <- data_clust %>% dplyr::select(-latitude, -longitude)

#summary(lm(nrml_avg_reviews~ neighbourhood, data = new_data_clust))

mod<- lm(nrml_avg_reviews ~ ., data = new_data_clust)

model_data <- model.matrix(mod)

#model_data

model_data <- cbind(new_data_clust$nrml_avg_reviews, model_data)

model_data <- data.frame(model_data)

#model_data

#View(model_data[,-2])

#memory.limit(size = 20000)
ref_brook <- model_data[,2]

#model_data
#dim(adjacency)

model_1_brook <- S.CARleroux(data = model_data[-2], formula = V1 ~ ., family="gaussian", W= adjacency, burnin=1000, n.sample=200000, thin=10)


model_2_brook <- S.glm(data =  model_data[-2], formula = V1 ~ ., family="gaussian", burnin=1000, n.sample=200000, thin=10)

summary(lm(data= new_data_clust, nrml_avg_reviews ~ .))


print(model_1_brook)
print(model_2_brook)
coef(model_1_brook) - coef(model_2_brook)



#Z.price <- as.matrix(dist(new_data_clust$price, diag=TRUE, upper=TRUE))

#model_3 <- S.CARdissimilarity(data = model_data[-2], formula = V1 ~ ., family="gaussian", W= adjacency, Z= list(Z.price =Z.price), W.binary = TRUE, burnin=1000, n.sample=100000, thin=10)
#model_3

```


```{r}
require(stringr)

data_br <- data.frame(str_remove(names(coef(model_1_bronx)), "neighbourhood"), unname(coef(model_1_bronx)), rep("Bronx", length(coef(model_1_bronx))))
names(data_br) <- c("Variables", "Value", "Borough")


data_br[,1] <-as.character(data_br[,1])
data_br[,2] <-as.numeric(as.character(data_br[,2]))
data_br[,3] <-as.character(data_br[,3])

data_queens <- data.frame(str_remove(names(coef(model_1_queens)), "neighbourhood"), unname(coef(model_1_queens)), rep("Queens", length(coef(model_1_queens))))
names(data_queens) <- c("Variables", "Value", "Borough")


data_queens[,1] <-as.character(data_queens[,1])
data_queens[,2] <-as.numeric(as.character(data_queens[,2]))
data_queens[,3] <-as.character(data_queens[,3])

data_brook <- data.frame(str_remove(names(coef(model_1_brook)), "neighbourhood"), unname(coef(model_1_brook)), rep("Brooklyn", length(coef(model_1_brook))))
names(data_brook) <- c("Variables", "Value", "Borough")


data_brook[,1] <-as.character(data_brook[,1])
data_brook[,2] <-as.numeric(as.character(data_brook[,2]))
data_brook[,3] <-as.character(data_brook[,3])

data_man <- data.frame(str_remove(names(coef(model_1_man)), "neighbourhood"), unname(coef(model_1_man)), rep("Manhattan", length(coef(model_1_man))))
names(data_man) <- c("Variables", "Value", "Borough")

data_r <- rbind(c("rho", 0.9072, "Bronx"), c("rho", 0.9277, "Manhattan"),  c("rho", 0.7474, "Queens"), c("rho", 0.7389, "Brooklyn"))
data_r <- data.frame(data_r)
names(data_r) <- c("Variables", "Value", "Borough")

data_man[,1] <-as.character(data_man[,1])
data_man[,2] <-as.numeric(as.character(data_man[,2]))
data_man[,3] <-as.character(data_man[,3])



data<- bind_rows(data_br, data_queens, data_brook, data_man)

saveRDS(data, "Coefficient_Data.rds")

```

```{r}
data <- readRDS("Coefficient_Data.rds")

data%>% filter(Variables != "(Intercept)" & Variables != "price" & Variables != "dist_to_subway") %>% filter(Borough == "Bronx") %>% ggplot(aes(x=Variables,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

data%>% filter(Variables != "(Intercept)" & Variables != "price" & Variables != "dist_to_subway") %>% filter(Borough == "Manhattan") %>% ggplot(aes(x=Variables,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

data%>% filter(Variables != "(Intercept)" & Variables != "price" & Variables != "dist_to_subway") %>% filter(Borough == "Queens") %>% ggplot(aes(x=Variables,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

data%>% filter(Variables != "(Intercept)" & Variables != "price" & Variables != "dist_to_subway") %>% filter(Borough == "Brooklyn") %>% ggplot(aes(x=Variables,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

data %>% filter(Variables == "price") %>% ggplot(aes(x=Borough,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

data_r  %>% ggplot(aes(x=Borough,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))

data %>% filter(Variables == "dist_to_subway") %>% ggplot(aes(x=Borough,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
