---
title: "Case study 1: Effect of chemical exposures on preterm birth"
author: 
- name: Olivier Binette, Brian Kundinger and Justin Weltz
date: 'January 23, 2020'
abstract: "abstract"
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
    citation_package: natbib
header-includes:
  - \usepackage{hyperref}
linestretch: 1
link-citations: yes
linkcolor: blue
fontfamily: mathpazo
fontsize: 10pt
bibliography: biblio.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(cowplot)
library(BAS)
source("prettyplot.R")
```

# 1. Introduction


## 1.1 Dataset and its limitations



# 2. Materials and methods

## 2.2 Data cleaning and transformation

TODO: OB

## 2.3 Text analysis
```{r}

```

## 2.4 Additional data

TODO: OB

## 2.5 CAR and glm models for neighborhood effect controlling for distance

- Neighborhood effect controlling for distance

- CAR model

- Hierarchical model
```{r}
require(car)
model_heir <- lmer(nrml_avg_reviews~ (1|neighbourhood_group/neighbourhood)+price +dist_to_subway, data = data_transformed)
summary(model_heir)
Anova(model_heir)
coef(model_heir)

data_transformed %>% 
  arrange(desc(price)) %>% 
  select(price)
```

## 2.6 Global hierarchical model to compare effects of different features

- Keyword importance
    - Take the 5 most important ones to feed in the RF.

- Global hierarchical model

- With all variables (excepted distance)


# 3. Results

- Graphical display of the results

- OB can help with the graphical display


# 4. Discussion


# Appendix

## EDA
TODO: OB

