---
title: 'Case study 1: Effect of chemical exposures on preterm birth'
author:
- name: Olivier Binette, Brian Kundinger and Justin Weltz
date: "January 23, 2020"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: svm-latex-ms.tex
  html_document:
    df_print: paged
fontfamily: mathpazo
fontsize: 10pt
header-includes: \usepackage{hyperref}
linestretch: 1
link-citations: yes
linkcolor: blue
fontfamily: mathpazo
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(cowplot)
library(BAS)
source("prettyplot.R")
```

# 1. Introduction


## 1.1 Dataset and its limitations



# 2. Materials and methods

## 2.2 Data cleaning and transformation

TODO: OB

## 2.3 Text analysis


## 2.4 Additional data

TODO: OB

# CAR Methods

In order to advise a new Airbnb owner on the best neighborhood to set up a property, we have to be careful to separate the neighborhood effect on popularity from auto-correlation over the spatial dimension. For example, Figure () and figure () demonstate two density patterns that would make an analysis of neighborhood popularity without controlling for distance problematic. The Theater District in New York City includes Times Square and many other major tourist attractions. In figure (), we can see that most of the Airbnb locations in Hell's Kitchen are concentrated next to the Theater Disctrict, meaning that the measured effect on popularity of being in the latter nieghborhood may be inflated because it is highly correlated with the desirability of the theater district. Figure (), depicts another interesting density pattern. We can see that although there are many Airbnb locations on the outskirts of Chinatown, there are very few in the heart of the neighborhood. This could cause Chinatown's popularity coefficient to be closely correlated with the neighborhoods that surround it. If we observe high popularity in this neighborhood and then advise a new Airbnb owner with this information, they could make a large strategic blunder by placing their property in middle of the neighborhood. This seems problematic!

Therefore, we will account for the density of Airbnb locations so that we can measure the "name brand effect" of neighborhoods on popularity. In order to control for the distance between properties, we will use the conditionally autor-egressive model proposed by Lareaux et al. in "_____". This Bayesian approach models spatial auto-correlation as a smooth function of distance using an adjacency matrix and a series of priors on distance effects specified below:

$$\phi_k| \phi_{-k}, W, \tau^2, \rho \sim N(\frac{\rho\sum_{i=1}^k w_{ki}\phi_i}{\rho\sum_{i=1}^k w_{ki} + 1-\rho}, \frac{\tau^2}{\rho\sum_{i=1}^k w_{ki} + 1-\rho})$$
$$\tau^2 \sim Inverse-Gamma(a,b)$$
$$\rho \sim Uniform(0,1)$$

We deternmine the distance between neighbours so that every property has a neighbor and the mean number of neighbours is around 30. The correlation between neighbor's spatial effects is determined by the equation (), where $\rho$ is a global parameter that determines the smoothing of the auto-correlation function (aka the magnitude and decay of correlation between neighboring properties). 

$$COR(\phi_k, \phi_j | \phi_{-kj}, W, \rho) = \frac{\rho w_{kj}}{\sqrt{(\rho \sum_{i=1}^k w_{ki} + 1 - \rho)(\rho \sum_{i=1}^k w_{ki} + 1 - \rho }}$$
Unfotunately, since the CAR model take a very long time to run on large datasets, we weren't able to model this spatial relationship for every observation and ended up running seperate analyses on each of the boroughs with 1000 randomly selected observations (in each borough). Lastly, we also controlled for price and distance to subway when measuring neighborhood effects in this model.

```{r, warning=FALSE, message=FALSE, echo= FALSE}
data <- readRDS("data_transformed.rds")
data_transformed <- readRDS("data_transformed.rds")
data %>% filter( neighbourhood == "Theater District" |neighbourhood == "Hell's Kitchen") %>% ggplot(aes(x  = latitude, y = longitude, color = neighbourhood)) + stat_density2d(aes(fill = ..level..), geom= "polygon") + theme(legend.position = "none") + ggtitle("Hell's Kitchen and Theater District Density")

data %>% filter(neighbourhood == "Chinatown") %>% ggplot(aes(x  = latitude, y = longitude)) + stat_density2d(aes(fill = ..level..), geom= "polygon") + theme(legend.position = "none") + ggtitle("Chinatown Density")

data %>% group_by(neighbourhood_group) %>% summarise(mean = mean(nrml_avg_reviews))
```

# CAR Results

Figure (), which depicts the $\rho$ parameter for each borough, clearly indicates that spatial auto-correlation is present in the dataset even after accounting for neighborhood effects. Even though the Figure (), () and () indicated a lot of diversity in effects and effect sizes based on neighborhoods, there are only a few coefficients whose $95\%$ posterior credible intervals do not include zero. Only Schuresville and Eastchester in the Bronx, Jamaica Hills and East Elmhurst in Queens have a "significant" effect. Since according, to Table (), Queens has the highest popularity baseline and East Elmhurt has a significant positive effect on top of this baseline (not exactly sure if I can say this because of refernce group), it seems like this is the best location for a new Airbnb owner to locate his property!

```{r, warning=FALSE, message=FALSE, echo= FALSE}

data_r <- rbind(c("rho", 0.9072, "Bronx"), c("rho", 0.9277, "Manhattan"),  c("rho", 0.7474, "Queens"), c("rho", 0.7389, "Brooklyn"))
data_r <- data.frame(data_r)
names(data_r) <- c("Variables", "Value", "Borough")

data <- readRDS("Coefficient_Data.rds")

data%>% filter(Variables != "(Intercept)" & Variables != "price" & Variables != "dist_to_subway") %>% filter(Borough == "Bronx") %>% ggplot(aes(x=Variables,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Bronx Coefficients")

data%>% filter(Variables != "(Intercept)" & Variables != "price" & Variables != "dist_to_subway") %>% filter(Borough == "Manhattan") %>% ggplot(aes(x=Variables,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Manhattan Coefficients")

data%>% filter(Variables != "(Intercept)" & Variables != "price" & Variables != "dist_to_subway") %>% filter(Borough == "Queens") %>% ggplot(aes(x=Variables,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Queens Coefficients")

data%>% filter(Variables != "(Intercept)" & Variables != "price" & Variables != "dist_to_subway") %>% filter(Borough == "Brooklyn") %>% ggplot(aes(x=Variables,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1))+ ggtitle("Brooklyn Coefficients")

data %>% filter(Variables == "price") %>% ggplot(aes(x=Borough,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Price Coefficients")

data_r  %>% ggplot(aes(x=Borough,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Rho Coefficients")

data %>% filter(Variables == "dist_to_subway") %>% ggplot(aes(x=Borough,y=Value)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ggtitle("Distance To Subw Coefficients")
```

# Hierarchical model

```{r}
require(car)
require(lme4)
#install.packages("car")
model_heir <- lmer(nrml_avg_reviews~ (1|neighbourhood_group/neighbourhood)+price +dist_to_subway, data = data_transformed)
summary(model_heir)
Anova(model_heir)
coef(model_heir)

```

## 2.6 Global hierarchical model to compare effects of different features

- Keyword importance
    - Take the 5 most important ones to feed in the RF.

- Global hierarchical model

- With all variables (excepted distance)


# 3. Results

- Graphical display of the results

- OB can help with the graphical display


# 4. Discussion


# Appendix

## EDA
TODO: OB

